The Privacy of Private Browsing

### 2013-12-13 finalproject/paper.tex
wrote to community and started applications

\documentclass[pdftex,letterpaper,12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage[doublespacing]{setspace}

@@

  \doublespacing
  \section{Introduction}
    \subsection{Browser Overview}
    Currently, the most popular browsers for the Windows and Linux families of
    operating systems are Mozilla Firefox, Google Chrome, and Microsoft 
    Internet Explorer. (Internet Explorer runs only on the Windows family of
    operating systems, whereas Firefox and Chrome run on both Windows and 
    Linux.) All three of these browsers have built-in private browsing modes.
    The features and protections provided by each of these private browsing
    modes are summarized below.\cite{verdi13}\cite{google13}\cite{ie13}

@@

    The private browsing modes of Firefox, Chrome, and Internet Explorer are
    designed with the intent of preventing users of the same computer from
    determining what someone was doing on that computer. They do not attempt
    to keep a user's internet activities hidden from that user's internet
    service provider (ISP), and they do not prevent websites from identifying
    that user.\cite{verdi13}\cite{google13}\cite{ie13}

    Users seeking this kind of anonymity should use the Tor browser, which
    employs onion routing to connect a user to a destination server. In this
    type of routing, a random path from the user to the destination is
    constructed, and content is encrypted at each point in the path.
    Furthermore, each point (known as a relay or node) only knows from which
    relay any given piece of network traffic immediately came and the next
    relay to which it is going. It does not know the original source of the
    network traffic or its final destination. This is what allows users to keep
    themselves and their activities anonymous using Tor in a way that the 
    traditional web browsers cannot.\cite{tor13}

@@

    \subsection{Known Issues with Private Browsing}
    Prior research in this area indicates that web browsers, even when used in
    their respective private browsing modes, can leave artifacts on a user's
    machine that can reveal their internet activities. %finish

  \section{To the Community}

  \section{Applications}

@@

  \singlespacing
  \begin{thebibliography}{9}
    \bibitem{verdi13}
      Verdi, Michael et al. ``Private Browsing.'' \emph{Mozilla Support}. 
      Mozilla Foundation, 29 Mar. 2013. Web. 10 Dec. 2013. 
      $<$\url{http://support.mozilla.org/en-US/kb/private-browsing-browse-web-
      without-saving-info}$>$.
    \bibitem{google13}
      ``Chrome Browser.'' \emph{Chrome}. Google, 18 Nov. 2013. Web. 10 Dec. 
      2013. $<$\url{http://www.google.com/intl/en/chrome/browser/
      features.html#privacy}$>$.
    \bibitem{ie13}
      ``InPrivate Browsing.'' \emph{Microsoft Windows}. Microsoft, 10 Dec. 
      2013. Web. 10 Dec. 2013. $<$\url{http://windows.microsoft.com/en-us/
      internet-explorer/products/ie-9/features/in-private}$>$.
    \bibitem{tor13}
      ``Tor Project: Overview.'' \emph{Tor}. Tor, 7 Dec. 2013. Web. 10 Dec. 
      2013. $<$\url{http://www.torproject.org/about/overview.html.en}$>$.

>>>>

\documentclass[pdftex,letterpaper,titlepage,12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage[doublespacing]{setspace}

@@

  \doublespacing
  \section{Introduction}
    \subsection{Browser Overview}
    Currently, the most popular browsers for the Windows family of operating 
    systems are Mozilla Firefox, Google Chrome, and Microsoft Internet 
    Explorer. All three of these browsers have built-in private browsing modes.
    The features and protections provided by each of these private browsing
    modes are summarized below.\cite{verdi13}\cite{google13}\cite{ie13}

@@

    \subsection{What Private Browsing Is Not}
    The private browsing modes of Firefox, Chrome, and Internet Explorer are
    designed with the intent of preventing users of the same computer from
    determining what someone was doing on that computer. They do not attempt
    to keep a user's internet activities hidden from that user's internet
    service provider (ISP), and they do not prevent websites from identifying
    that user.\cite{verdi13}\cite{google13}\cite{ie13} Users seeking this kind 
    of anonymity should use the Tor browser, which employs onion routing to 
    connect a user to a destination server. In this type of routing, a random 
    path from the user to the destination is constructed, and content is 
    encrypted at each point in the path. Furthermore, each point (known as a 
    relay or node) only knows from which relay any given piece of network 
    traffic immediately came and the next relay to which it is going. It does 
    not know the original source of the network traffic or its final 
    destination. This is what allows users to keep themselves and their 
    activities anonymous using Tor in a way that the traditional web browsers 
    cannot.\cite{tor13}

@@

  \section{To the Community}
  There are many misconceptions about private browsing. Some believe that it
  prevents an internet service provider, network administrator, or attackers
  engaged in packet sniffing from linking a user's internet activities to his
  or her identity. It does not. Any and all network packets leaving the user's
  machine contain information such as the user's IP address, which can be used
  to determine his or her location and/or identity. Others think that private
  browsing sessions leave absolutely no trace of their activities on their
  local machines. As the next section of this paper will describe, this is also
  false. Still others think that private browsing will prevent the National
  Security Agency from tracking them on social media. It certainly does not.
  This paper will shed some light on what private browsing sessions can and
  cannot do, allowing internet users to think twice before exploring the web.

  \section{Applications: Forensics}
  One of the biggest problems with private browsing sessions is that artifacts
  remain on a machine after the user exits his or her internet browser. These
  artifacts can include logon information for websites, browsing history,
  and digital media such as images and videos---all items that you would expect
  a private browsing session to keep private.\cite{ohana13}

  This section will first summarize locations on a Windows machine where
  private browsing artifacts might be found. An overview of what specific
  artifacts were found for each browser using different forensic techniques
  will follow. The use of SQLite to investigate specific browser artifacts will
  then be discussed.

    \subsection{Where To Look}

    Focused analysis of the hard drive itself can reveal the most artifacts.
    One private browsing experiment in which logon information, browser
    history, and cached images were recovered obtained most of the artifacts
    from portions of the hard disk known as \emph{free space} and \emph{slack
    space}. Free space refers to a group of hard drive sectors (called a
    \emph{cluster} that is not allocated to any particular file. Slack space, 
    on the other hand, refers to the space between the end of a file and the 
    end of the cluster in which it is stored. Hard drive clusters are of a 
    fixed size determined by the operating system. Most of the time, when a 
    user saves a file to his or her hard drive, the file is not exactly the
    same size as the cluster in which the operating system puts it.
    Furthermore, when a user ``deletes'' a file from his or her hard drive, the
    file is not really deleted---it is simply marked as available to be
    overwritten if necessary. If a file is eventually stored on the hard drive
    in a cluster that used to be home to a larger (now ``deleted'') file,
    leftover data from the old file will still exist at the end of that
    cluster.

    \subsection{Firefox}

    \subsection{Google Chrome}

    \subsection{Internet Explorer}
    Internet Explorer leaves the most artifacts behind when its InPrivate
    Browsing mode terminates.\cite{ohana13}

    \subsection{Tor}

    \subsection{Forensic Software}

@@

  \singlespacing
  \begin{thebibliography}{9}
    \bibitem{verdi13}
      Verdi, Michael et al. ``Private Browsing.'' \emph{Mozilla Support}. 
      Mozilla Foundation, 29 Mar. 2013. Web. 10 Dec. 2013. 
      $<$\url{http://support.mozilla.org/en-US/kb/private-browsing-browse-web-
      without-saving-info}$>$.
    \bibitem{google13}
      ``Chrome Browser.'' \emph{Chrome}. Google, 18 Nov. 2013. Web. 10 Dec. 
      2013. $<$\url{http://www.google.com/intl/en/chrome/browser/
      features.html#privacy}$>$.
    \bibitem{ie13}
      ``InPrivate Browsing.'' \emph{Microsoft Windows}. Microsoft, 10 Dec. 
      2013. Web. 10 Dec. 2013. $<$\url{http://windows.microsoft.com/en-us/
      internet-explorer/products/ie-9/features/in-private}$>$.
    \bibitem{tor13}
      ``Tor Project: Overview.'' \emph{Tor}. Tor, 7 Dec. 2013. Web. 10 Dec. 
      2013. $<$\url{http://www.torproject.org/about/overview.html.en}$>$. 
    \bibitem{ohana13}
      Ohana, Donny, and Narasimha Shashidhar. ``Do Private and Portable Web 
      Browsers Leave Incriminating Evidence? A Forensic Analysis of Residual 
      Artifacts from Private and Portable Web Browsing Sessions.'' IEEE CS 
      Security and Privacy Workshops (SPW), The Westin St. Francis, 
      San Francisco, CA. 23-24 May 2013. Web. 9 Dec. 2013. $<$\url{http://www.
      ieee-security.org/TC/SPW2013/papers/data/5017a135.pdf}$>$
